### 2022-05-17 supplement.Rmd
Move methods tables to the supplement

Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]). However, we decided to assume a correlation of $r  = .50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descriptives$n_experiments` experiments. This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002]. To  evaluate the robustness of our Bayesian meta-analytic model against the assumption of a correlation of $r  = .50$ we ran a sensitivity analysis (Supplementary Table\ \@ref(tab:tabs4)).

@@

We used trim-and-fill analysis and selection models to examine if and how our meta-analytic results would change under different degrees of publication bias. For both of these types of models, we used a simplified two-level version of our frequentist three-level model as a basis. In our first step, we computed a trim-and-fill model [@duval2000] by imputing possible effect sizes of non-published experiments. This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables 8 and 9).

In our next step, we used selection models to approximate the process by which experiments got selected into the meta-analysis. These models were based on the assumption that experiments yielding significant effects (i.e., small *p*-values) are more likely to get published. Specifically, we ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30. Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005]. These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables 8 and 9).

@@

@@

  # Create table for the meta-analysis of mental rotation performance
  sens %>%
    select(res, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res, manipulation_name, manipulation_value) {
      print_res_table(
        res,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs5
  write_csv(tabs5, file = here(tables_dir, "tabs5_sens_meta.csv"))

  # Create table for the meta-regression of mental rotation performance
  sens %>%
    select(
      res_reg, manipulation_name, manipulation_value
    ) %>%
    pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
      print_res_reg_table(
        res_reg,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs6
  write_csv(tabs6, file = here(tables_dir, "tabs6_sens_reg.csv"))

  # Create table for the meta-analysis of gender differences
  sens %>%
    filter(!map_lgl(res_gender, is.null)) %>%
    select(res_gender, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
      print_res_table(
        res_gender,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs7
  write_csv(tabs7, file = here(tables_dir, "tabs7_sens_gender.csv"))
}
```

@@

```{r, tabs5, include=TRUE}
# Load sensitivity analysis table from file
tabs5 <- read_csv(
  here(tables_dir, "tabs5_sens_meta.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

# Add footnotes
colnames(tabs5)[6] <- str_c(colnames(tabs5)[6], "\\textsuperscript{a}")
tabs5$` `[8] <- str_c(tabs5$` `[8], "\\textsuperscript{b}")
tabs5$` `[9] <- str_c(tabs5$` `[9], "\\textsuperscript{c}")
tabs5$` `[10] <- str_c(tabs5$` `[10], "\\textsuperscript{d}")
tabs5$` `[11] <- str_c(tabs5$` `[11], "\\textsuperscript{e}")

# Display the table
apa_table(
  tabs5,
  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = intraclass correlation, ",
    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrr"
)
```

```{r, tabs6, include=TRUE}
# Load sensitivity analysis table from file
tabs6 <- read_csv(
  here(tables_dir, "tabs6_sens_reg.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

# Add footnotes
tabs6$` `[8] <- str_c(tabs6$` `[8], "\\textsuperscript{a}")
tabs6$` `[9] <- str_c(tabs6$` `[9], "\\textsuperscript{b}")
tabs6$` `[10] <- str_c(tabs6$` `[10], "\\textsuperscript{c}")
tabs6$` `[11] <- str_c(tabs6$` `[11], "\\textsuperscript{d}")

# Display the table
apa_table(
  tabs6,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{b} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{c} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{d} = an informative (Student-$t$) prior on the standard deviations."
  ),
  font_size = "scriptsize", landscape = TRUE, escape = FALSE,
  align = "llrrrrrrr"
)
```

```{r, tabs7, include=TRUE}
# Load sensitivity analysis table from file
tabs7 <- read_csv(
  here(tables_dir, "tabs7_sens_gender.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

# Add footnotes
colnames(tabs7)[6] <- str_c(colnames(tabs7)[6], "\\textsuperscript{a}")
tabs7$` `[1] <- str_c(tabs7$` `[1], "\\textsuperscript{b}")
tabs7$` `[2] <- str_c(tabs7$` `[2], "\\textsuperscript{c}")
tabs7$` `[3] <- str_c(tabs7$` `[3], "\\textsuperscript{d}")
tabs7$` `[4] <- str_c(tabs7$` `[4], "\\textsuperscript{e}")

# Display the table
apa_table(
  tabs7,
  caption = "Sensitivity analyses for the meta-analysis of gender differences",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = intraclass correlation, ",
    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrrrrr"
)
```

@@

# Save the tables
tabs8 <- tabs_correction$meta
tabs9 <- tabs_correction$gender
write_csv(tabs8, file = here(tables_dir, "tabs8_correction_meta.csv"))
write_csv(tabs9, file = here(tables_dir, "tabs9_correction_gender.csv"))
```

```{r, tabs8, include=TRUE}
# Add footnotes
colnames(tabs8)[4] <- str_c(colnames(tabs8)[4], "\\textsuperscript{a}")
colnames(tabs8)[7] <- str_c(colnames(tabs8)[7], "\\textsuperscript{b}")

# Display the table
apa_table(
  tabs8,
  caption = "Publication bias correction for the meta-analysis of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = standard error, ",
    "\\textsuperscript{b} = 95\\% confidence interval."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrrr"
)
```

```{r, tabs9, include=TRUE}
# Add footnotes
colnames(tabs9)[4] <- str_c(colnames(tabs9)[4], "\\textsuperscript{a}")
colnames(tabs9)[7] <- str_c(colnames(tabs9)[7], "\\textsuperscript{b}")

# Display the table
apa_table(
  tabs9,
  caption = "Publication bias correction for the meta-analysis of gender differences",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = standard error, ",
    "\\textsuperscript{b} = 95\\% confidence interval."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrrr",
)
```

>>>>

Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]). However, we decided to assume a correlation of $r  = .50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descriptives$n_experiments` experiments. This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002]. To  evaluate the robustness of our Bayesian meta-analytic model against the assumption of a correlation of $r  = .50$ we ran a sensitivity analysis (Supplementary Tables\ \@ref(tab:tabs7) and \@ref(tab:tabs8)).

@@

We used trim-and-fill analysis and selection models to examine if and how our meta-analytic results would change under different degrees of publication bias. For both of these types of models, we used a simplified two-level version of our frequentist three-level model as a basis. In our first step, we computed a trim-and-fill model [@duval2000] by imputing possible effect sizes of non-published experiments. This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11); Supplementary Fig.\ \@ref(fig:figs4)).

In our next step, we used selection models to approximate the process by which experiments got selected into the meta-analysis. These models were based on the assumption that experiments yielding significant effects (i.e., small *p*-values) are more likely to get published. Specifically, we ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30. Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005]. These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables\ \@ref(tab:tabs10) and \@ref(tab:tabs11)).

@@

\renewcommand{\arraystretch}{1.30}
\scriptsize
\LTcapwidth=\textwidth

+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ Available statistics                                       | Conversion to standardized mean difference (Hedges' $g$)                                    |
+================================================================+=============================================================================================+
| \ \ (1\) Cohen's $d$ and sample size                           | ${df}=2(n-1)$;\quad                                                                         |
| [@goulet-pelletier2018; @hedges1985]                           | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$; |
|                                                                | \quad $g_\text{rotation}=d\cdot{J}({df})$                                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (2\) $t$-statistic and sample size [@rosenthal1991]        | $d=\frac{t}{\sqrt{n}}$;\quad then (1)                                                       |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (3\) $F$-statistic and sample size [@lakens2013]           | $t=\sqrt{f}$;\quad then (2\)                                                                |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (4\) Mean difference between conditions [@lakens2013]      | $d=\frac{m_\text{diff}}{{SD}_\text{diff}}$;\quad then (1)                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (5\) Mean looking time and ${SD}$ per condition            | ${SD}_\text{av}=\sqrt{\frac{{SD}_\text{novel}^2+{SD}_\text{familiar}^2}{2}}$;\quad          |
| [@cumming2012]                                                 | $d=\frac{m_\text{novel}-m_\text{familiar}}{{SD}_\text{av}}$;\quad then (1)                  |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+
| \ \ (6\) Mean novelty preference score [@lakens2013]           | $d=\frac{m_\text{pref}}{{SD}_\text{pref}}$;\quad then (1)                                   |
+----------------------------------------------------------------+---------------------------------------------------------------------------------------------+

Table: (\#tab:tabs5) Effect size conversion for the meta-analysis of mental rotation performance

+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ Available statistics               | Conversion to standardized mean difference (Hedges' $g$)                                         |
+========================================+==================================================================================================+
| \ \ (1\) Cohen's $d$ and group sizes   | ${df}=n_\text{female}+n_\text{male}-1$; \quad                                                    |
| [@goulet-pelletier2018; @hedges1985]   | $J({df})=\frac{\Gamma(\frac{1}{2}{df})}{\sqrt{\frac{{df}}{2}}\Gamma(\frac{1}{2}({df}-1))}$;\quad |
|                                        | $g_\text{gender}=d\cdot{J({df})}$                                                                |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (2\) $t$-statistic and group sizes | $d=t\sqrt{\frac{1}{n_\text{female}}+\frac{1}{n_\text{male}}}$;\quad then (1)                     |
| [@lakens2013]                          |                                                                                                  |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (3\) $F$-statistic and group sizes | $t=\sqrt{f}$;\quad then (2\)                                                                     |
| [@lakens2013]                          |                                                                                                  |
+----------------------------------------+--------------------------------------------------------------------------------------------------+
| \ \ (4\) Mean differences between\     | ${SD}_\text{pooled}=\sqrt{\frac{(n_\text{female}-1){SD}_\text{female}^2                          |
| \ \ conditions or preference scores    | +(n_\text{male}-1){SD}_\text{male}^2}{df}}$;\quad                                                |
| [@lakens2013]                          | $d=\frac{m_\text{female}-m_\text{male}}{{SD}_\text{pooled}}$;\quad then (1)                      |
+----------------------------------------+--------------------------------------------------------------------------------------------------+

Table: (\#tab:tabs6) Effect size conversion for the meta-analysis of gender differences

\normalsize

@@

  # Create table for the meta-analysis of mental rotation performance
  sens %>%
    select(res, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res, manipulation_name, manipulation_value) {
      print_res_table(
        res,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs7
  write_csv(tabs7, file = here(tables_dir, "tabs7_sens_meta.csv"))

  # Create table for the meta-regression of mental rotation performance
  sens %>%
    select(
      res_reg, manipulation_name, manipulation_value
    ) %>%
    pmap_dfr(function(res_reg, manipulation_name, manipulation_value) {
      print_res_reg_table(
        res_reg,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs8
  write_csv(tabs8, file = here(tables_dir, "tabs8_sens_reg.csv"))

  # Create table for the meta-analysis of gender differences
  sens %>%
    filter(!map_lgl(res_gender, is.null)) %>%
    select(res_gender, manipulation_name, manipulation_value) %>%
    pmap_dfr(function(res_gender, manipulation_name, manipulation_value) {
      print_res_table(
        res_gender,
        label_1 = manipulation_name, label_2 = manipulation_value,
        label_col_1 = "Manipulation", label_col_2 = " "
      )
    }) -> tabs9
  write_csv(tabs9, file = here(tables_dir, "tabs9_sens_gender.csv"))
}
```

@@

```{r, tabs7, include=TRUE}
# Load sensitivity analysis table from file
tabs7 <- read_csv(
  here(tables_dir, "tabs7_sens_meta.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

# Add footnotes
colnames(tabs7)[6] <- str_c(colnames(tabs7)[6], "\\textsuperscript{a}")
tabs7$` `[8] <- str_c(tabs7$` `[8], "\\textsuperscript{b}")
tabs7$` `[9] <- str_c(tabs7$` `[9], "\\textsuperscript{c}")
tabs7$` `[10] <- str_c(tabs7$` `[10], "\\textsuperscript{d}")
tabs7$` `[11] <- str_c(tabs7$` `[11], "\\textsuperscript{e}")

# Display the table
apa_table(
  tabs7,
  caption = "Sensitivity analyses for the meta-analysis of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = intraclass correlation, ",
    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
  ),
  placement = "hb", font_size = "scriptsize", escape = FALSE, align = "llrrrr"
)
```

```{r, tabs8, include=TRUE}
# Load sensitivity analysis table from file
tabs8 <- read_csv(
  here(tables_dir, "tabs8_sens_reg.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

# Add footnotes
tabs8$` `[8] <- str_c(tabs8$` `[8], "\\textsuperscript{a}")
tabs8$` `[9] <- str_c(tabs8$` `[9], "\\textsuperscript{b}")
tabs8$` `[10] <- str_c(tabs8$` `[10], "\\textsuperscript{c}")
tabs8$` `[11] <- str_c(tabs8$` `[11], "\\textsuperscript{d}")

# Display the table
apa_table(
  tabs8,
  caption = "Sensitivity analyses for the meta-regression of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{b} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{c} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{d} = an informative (Student-$t$) prior on the standard deviations."
  ),
  font_size = "scriptsize", landscape = TRUE, escape = FALSE,
  align = "llrrrrrrr"
)
```

```{r, tabs9, include=TRUE}
# Load sensitivity analysis table from file
tabs9 <- read_csv(
  here(tables_dir, "tabs9_sens_gender.csv"),
  col_types = "c", na = character(), trim_ws = FALSE
)

# Add footnotes
colnames(tabs9)[6] <- str_c(colnames(tabs9)[6], "\\textsuperscript{a}")
tabs9$` `[1] <- str_c(tabs9$` `[1], "\\textsuperscript{b}")
tabs9$` `[2] <- str_c(tabs9$` `[2], "\\textsuperscript{c}")
tabs9$` `[3] <- str_c(tabs9$` `[3], "\\textsuperscript{d}")
tabs9$` `[4] <- str_c(tabs9$` `[4], "\\textsuperscript{e}")

# Display the table
apa_table(
  tabs9,
  caption = "Sensitivity analyses for the meta-analysis of gender differences",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = intraclass correlation, ",
    "\\textsuperscript{b} = an uninformative (uniform) prior on the mean effect, ",
    "\\textsuperscript{c} = an informative (normal) prior on the mean effect, ",
    "\\textsuperscript{d} = an uninformative (uniform) prior on the standard deviations, ",
    "\\textsuperscript{e} = an informative (Student-$t$) prior on the standard deviations."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrrrrr"
)
```

@@

# Save the tables
tabs10 <- tabs_correction$meta
tabs11 <- tabs_correction$gender
write_csv(tabs10, file = here(tables_dir, "tabs10_correction_meta.csv"))
write_csv(tabs11, file = here(tables_dir, "tabs11_correction_gender.csv"))
```

```{r, tabs10, include=TRUE}
# Add footnotes
colnames(tabs10)[4] <- str_c(colnames(tabs10)[4], "\\textsuperscript{a}")
colnames(tabs10)[7] <- str_c(colnames(tabs10)[7], "\\textsuperscript{b}")

# Display the table
apa_table(
  tabs10,
  caption = "Publication bias correction for the meta-analysis of mental rotation performance",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = standard error, ",
    "\\textsuperscript{b} = 95\\% confidence interval."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrrr"
)
```

```{r, tabs11, include=TRUE}
# Add footnotes
colnames(tabs11)[4] <- str_c(colnames(tabs11)[4], "\\textsuperscript{a}")
colnames(tabs11)[7] <- str_c(colnames(tabs11)[7], "\\textsuperscript{b}")

# Display the table
apa_table(
  tabs11,
  caption = "Publication bias correction for the meta-analysis of gender differences",
  note = str_c(
    "\\scriptsize",
    "\\textsuperscript{a} = standard error, ",
    "\\textsuperscript{b} = 95\\% confidence interval."
  ),
  font_size = "scriptsize", escape = FALSE, align = "llrrrrr",
)
```

\newpage
